### 2019-11-05 thesis/txt/5-study.tex
describe more results for kws and all techniques, draft out conclusions section

For each of our evaluation runs we measure the desired vs. actual output lines of the chunk retrieval.
The desired output is given by the output of the test I/O example, which acts as the oracle for our evaluation.
From this we obtain true/false positives/negatives and calculate precision, recall and accuracy, which we use to answer \textbf{RQ2.2}.
We register the number of examples used as configuration for each run to answer \textbf{RQ2.1} and their structural categories to answer \textbf{RQ2.3}.
\todo{mention / explain retrival size facto}

@@

\begin{figure}[htbp]
	\centering
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/failure-reason-PBE.pdf}
		\caption{Results of chunk retrieval with PBE}
		\label{fig:failure-reason-PBE}
	\end{minipage}\hfill
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/failure-reason-categorycount-PBE.pdf}
		\caption{Results of chunk retrieval with PBE for numbers of categories present in configuring I/O examples}
		\label{fig:failure-reason-categorycount-PBE}
	\end{minipage}
\end{figure}
\begin{figure}[htbp]
	\centering
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/precision-extraction-result-PBE.pdf}
		\caption{Precision chunk retrieval with PBE for increasing count of configuring I/O examples}
		\label{fig:precision-extraction-result-PBE}
	\end{minipage}\hfill
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/xxx.pdf}
		\caption{xxx}
		\label{fig:xxx}
	\end{minipage}
\end{figure}
\subsection{Regular Expression Program Synthesis by Example (PBE)}
Figure~\ref{fig:failure-reason-PBE} shows the results of the PBE runs in our evaluation.
Out of the 400 runs, 5 per each one of the 80 example sets, PBE extracted all the desired lines in 138 cases.
Figure \ref{fig:failure-reason-PBE} shows that in 89 further cases a program was also successfully synthesized, though in 59 cases the synthesized program yielded no output at all.
In 30 cases the synthesized program did not extract all of the desired lines, though still had an average recall of 28\%.
In 173 cases the PROSE program synthesis could not synthesize a singular regular expression program that satisfies all of the configuring I/O examples.

@@

\begin{figure}[htbp]
	\centering
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-examplecount-TS.pdf}
		\caption{Paieya}
		\label{fig:recall-precision-examplecount-TS}
	\end{minipage}\hfill
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-categorycount-TS.pdf}
		\caption{nei}
		\label{fig:recall-precision-categorycount-TS}
	\end{minipage}
\end{figure}
\begin{figure}[htbp]
	\centering
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/contextsizefactor-precision-recall-TS.pdf}
		\caption{neind}
		\label{fig:contextsizefactor-precision-recall-TS}
	\end{minipage}\hfill
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/xxx.pdf}
		\caption{xxx}
		\label{fig:xxx}
	\end{minipage}
\end{figure}

@@

Figure \ref{fig:contextsizefactor-precision-recall-TS} shows the impact of the retrieval size factor on precision and accuracy of chunk retrieval runs with CTS.
The precision ranges from 52\% when retrieving half expected number of lines to 25\% when 2.5 times the expected number of lines.
The recall ranges

% \begin{figure}[htbp]
% 	\centering
% 	\begin{minipage}{0.45\textwidth}
% 		\centering
% 		\includegraphics[width=\textwidth, clip]{img/big-study/success-examples-TS.pdf}
% 		\caption{Successful Extractions per Number of Examples for TS}
% 		\label{fig:success-examples-ts}
% 	\end{minipage}\hfill
% 	\begin{minipage}{0.45\textwidth}
% 		\centering
% 		\includegraphics[width=\textwidth, clip]{img/big-study/precision-TS.pdf}
% 		\caption{Precision of Extractions per Number of Examples for TS}
% 		\label{fig:precision-ts}
% 	\end{minipage}
% \end{figure}
% \begin{figure}[htbp]
% 	\centering
% 	\begin{minipage}{0.45\textwidth}
% 		\centering
% 		\includegraphics[width=\textwidth, clip]{img/big-study/precision-categorycount-examplecount-TS.pdf}
% 		\caption{Precision of TS Extractions by CategoryCount}
% 		\label{fig:precision-categorycount-examplecount-ts}
% 	\end{minipage}\hfill
% 	\begin{minipage}{0.45\textwidth}
% 		\centering
% 		\includegraphics[width=\textwidth, clip]{img/big-study/xxx.pdf}
% 		\caption{xxx}
% 		\label{fig:xxx}
% 	\end{minipage}
% \end{figure}

% \subsubsection{Success-Rate}
% \subsubsection{Precision}
% \subsubsection{Example Categories}

\subsection{Keyword Search (KWS)}

% \begin{figure}[htbp]
% 	\centering
% 	\begin{minipage}{0.45\textwidth}
% 		\centering
% 		\includegraphics[width=\textwidth, clip]{img/big-study/success-examples-SKWS.pdf}
% 		\caption{Successful Extractions per Number of Examples for SKWS}
% 		\label{fig:success-examples-skws}
% 	\end{minipage}\hfill
% 	\begin{minipage}{0.45\textwidth}
% 		\centering
% 		\includegraphics[width=\textwidth, clip]{img/big-study/precision-SKWS.pdf}
% 		\caption{Precision of Extractions per Number of Examples for SKWS}
% 		\label{fig:precision-skws}
% 	\end{minipage}
% \end{figure}
% \begin{figure}[htbp]
% 	\centering
% 	\begin{minipage}{0.45\textwidth}
% 		\centering
% 		\includegraphics[width=\textwidth, clip]{img/big-study/precision-categorycount-examplecount-SKWS.pdf}
% 		\caption{Precision of SKWS Extractions by CategoryCount}
% 		\label{fig:precision-categorycount-examplecount-skws}
% 	\end{minipage}\hfill
% 	\begin{minipage}{0.45\textwidth}
% 		\centering
% 		\includegraphics[width=\textwidth, clip]{img/big-study/xxx.pdf}
% 		\caption{xxx}
% 		\label{fig:xxx}
% 	\end{minipage}
% \end{figure}

% \subsubsection{Success-Rate}
% \subsubsection{Precision}
% \subsubsection{Example Categories}

% \subsection{Random Line Retrieval (RLR)}

% \begin{figure}[htbp]
% 	\centering
% 	\begin{minipage}{0.45\textwidth}
% 		\centering
% 		\includegraphics[width=\textwidth, clip]{img/big-study/success-examples-RLR.pdf}
% 		\caption{Successful Extractions per Number of Examples for RLR}
% 		\label{fig:success-examples-rlr}
% 	\end{minipage}\hfill
% 	\begin{minipage}{0.45\textwidth}
% 		\centering
% 		\includegraphics[width=\textwidth, clip]{img/big-study/precision-RLR.pdf}
% 		\caption{Precision of Extractions per Number of Examples for RLR}
% 		\label{fig:precision-rlr}
% 	\end{minipage}
% \end{figure}
% \begin{figure}[htbp]
% 	\centering
% 	\begin{minipage}{0.45\textwidth}
% 		\centering
% 		\includegraphics[width=\textwidth, clip]{img/big-study/precision-categorycount-examplecount-RLR.pdf}
% 		\caption{Precision of RLR Extractions by CategoryCount}
% 		\label{fig:precision-categorycount-examplecount-rlr}
% 	\end{minipage}\hfill
% 	\begin{minipage}{0.45\textwidth}
% 		\centering
% 		\includegraphics[width=\textwidth, clip]{img/big-study/xxx.pdf}
% 		\caption{xxx}
% 		\label{fig:xxx}
% 	\end{minipage}
% \end{figure}

% For completion this section reports the results for the random line retrieval technique, explained in detail in Section \ref{sec:}

% \subsubsection{Success-Rate}
% \subsubsection{Precision}
% \subsubsection{Example Categories}

\subsection{Comparing All Techniques}
% \begin{figure}[htbp]
% 	\centering
% 	\begin{minipage}{0.45\textwidth}
% 		\centering
% 		\includegraphics[width=\textwidth, clip]{img/big-study/success-all.pdf}
% 		\caption{Successful Extractions for all Techniques Compared}
% 		\label{fig:success-all}
% 	\end{minipage}\hfill
% 	\begin{minipage}{0.45\textwidth}
% 		\centering
% 		\includegraphics[width=\textwidth, clip]{img/big-study/precision-all.pdf}
% 		\caption{Precision of Extractions for all Techniques Compared}
% 		\label{fig:precision-all}
% 	\end{minipage}
% \end{figure}

% \begin{figure}[htbp]
% 	\centering
% 	\begin{minipage}{0.45\textwidth}
% 		\centering
% 		\includegraphics[width=\textwidth, clip]{img/big-study/precision-category-singularity-all.pdf}
% 		\caption{\todo{todo}}
% 		\label{fig:precision-category-singularity-all}
% 	\end{minipage}\hfill
% 	\begin{minipage}{0.45\textwidth}
% 		\centering
% 		\includegraphics[width=\textwidth, clip]{img/big-study/single-cateogry-precision-all.pdf}
% 		\caption{\todo{todo}}
% 		\label{fig:single-cateogry-precision-all}
% 	\end{minipage}
% \end{figure}

% \begin{figure}[htbp]
% 	\centering
% 	\begin{minipage}{0.45\textwidth}
% 		\centering
% 		\includegraphics[width=\textwidth, clip]{img/big-study/precision-categorycount-examplecount-all.pdf}
% 		\caption{\todo{todo}}
% 		\label{fig:precision-categorycount-examplecount-all}
% 	\end{minipage}\hfill
% 	\begin{minipage}{0.45\textwidth}
% 		\centering
% 		\includegraphics[width=\textwidth, clip]{img/big-study/xxx.pdf}
% 		\caption{\todo{todo}}
% 		\label{fig:xxx}
% 	\end{minipage}
% \end{figure}

% \subsubsection{Success-Rate}
% \subsubsection{Precision}
% \subsubsection{Example Categories}

% \section{Discussion}
% \todo{draw decision tree}

% interpret results - when should PROSE be used? - when should text similarity be used? - when should keyword search be used? - answer RQ about PROSE \& other techniques
\section{Threats to Validity}
%chronologically selected examples -> very specific view

>>>>

For each of our evaluation runs we measure the desired vs. actual output lines of the chunk retrieval.
The desired output is given by the output of the test I/O example, which acts as the oracle for our evaluation.
From this we obtain true/false positives/negatives and calculate precision, recall and accuracy, which we use to answer \textbf{RQ2.2}.
We register the number of examples used as configuration for each run to answer \textbf{RQ2.1} and their structural categories to answer \textbf{RQ2.3}.
\todo{mention / explain retrival size factor}
\todo{introduce special words / measurements like ``successful''?}

@@

\begin{figure}[htbp]
	\centering
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/failure-reason-PBE.pdf}
		\caption{Results of chunk retrieval with PBE}
		\label{fig:failure-reason-PBE}
	\end{minipage}\hfill
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/failure-reason-categorycount-PBE.pdf}
		\caption{Results of chunk retrieval with PBE for numbers of categories present in configuring I/O examples}
		\label{fig:failure-reason-categorycount-PBE}
	\end{minipage}
\end{figure}
\begin{figure}[htbp]
	\centering
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/precision-extraction-result-PBE.pdf}
		\caption{Precision of chunk retrieval with PBE for increasing count of configuring I/O examples}
		\label{fig:precision-extraction-result-PBE}
	\end{minipage}\hfill
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/xxx.pdf}
		\caption{xxx}
		\label{fig:xxx}
	\end{minipage}
\end{figure}
\subsection{Regular Expression Program Synthesis by Example (PBE)}
Figure~\ref{fig:failure-reason-PBE} shows the results of the PBE runs in our evaluation.
Out of the 400 runs, 5 per each one of the 80 example sets, PBE extracted all the desired lines in 138 cases.
Figure \ref{fig:failure-reason-PBE} shows that in 89 further cases a program was also successfully synthesized, though in 59 cases the synthesized program yielded no output at all.
In 30 cases the synthesized program did not extract all of the desired lines, though still had an average recall of 28\%.
In 173 cases the PROSE program synthesis could not synthesize a singular regular expression program that satisfies all of the configuring I/O examples.

@@

\begin{figure}[htbp]
	\centering
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-examplecount-TS.pdf}
		\caption{Precision and recall of chunk retrieval with CTS for increasing count of configuring I/O examples}
		\label{fig:recall-precision-examplecount-TS}
	\end{minipage}\hfill
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-categorycount-TS.pdf}
		\caption{Precision and recall of chunk retrieval with CTS for increasing number of categories present in the configuring I/O examples}
		\label{fig:recall-precision-categorycount-TS}
	\end{minipage}
\end{figure}
\begin{figure}[htbp]
	\centering
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/contextsizefactor-precision-recall-TS.pdf}
		\caption{Precision and recall of chunk retrieval with CTS compared to retrieval size factors}
		\label{fig:contextsizefactor-precision-recall-TS}
	\end{minipage}\hfill
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/xxx.pdf}
		\caption{xxx}
		\label{fig:xxx}
	\end{minipage}
\end{figure}

@@

Figure \ref{fig:contextsizefactor-precision-recall-TS} shows the impact of the retrieval size factor on precision and accuracy of chunk retrieval runs with CTS.
The precision ranges from 52\% when retrieving half expected number of lines to 25\% when 2.5 times the expected number of lines.
The recall ranges from 30\% to 55\%.

\begin{figure}[htbp]
	\centering
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-examplecount-SKWS.pdf}
		\caption{Precision and recall of chunk retrieval with SKWS for increasing count of configuring I/O examples}
		\label{fig:recall-precision-examplecount-SKWS}
	\end{minipage}\hfill
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-categorycount-SKWS.pdf}
		\caption{Precision and recall of chunk retrieval with SKWS for increasing number of categories present in the configuring I/O examples}
		\label{fig:recall-precision-categorycount-SKWS}
	\end{minipage}
\end{figure}
\begin{figure}[htbp]
	\centering
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/contextsizefactor-precision-recall-SKWS.pdf}
		\caption{Precision and recall of chunk retrieval with SKWS compared to retrieval size factors}
		\label{fig:contextsizefactor-precision-recall-SKWS}
	\end{minipage}\hfill
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/xxx.pdf}
		\caption{xxx}
		\label{fig:xxx}
	\end{minipage}
\end{figure}

\subsection{Keyword Search (KWS)}
\todo{plot accuracy? especiall against retrieval size factor, could be that we are soon extracting all/most avaliable lines}
Figure \ref{fig:recall-precision-examplecount-SKWS} presents precision and recall of chunk retrieval using SKWS in our study for different numbers of configuring I/O examples.
The recall jumps from 53\% to over 70\% for more than two configuring I/O examples, while the precision stays constant at around 16\%.

Figure \ref{fig:recall-precision-categorycount-SKWS} shows the same measurements for different category counts in the configuring I/O examples.
There is no clear trend visible in precision and recall for an increasing amount of categories in the configuring I/O examples

Figure \ref{fig:contextsizefactor-precision-recall-SKWS} shows the impact of the retrieval size factor on precision and accuracy of chunk retrieval runs with SKWS.
The precision ranges from 19\% when retrieving half expected number of lines to 10\% when 2.5 times the expected number of lines.
The recall ranges from 58\% to 75\%.

\begin{figure}[htbp]
	\centering
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/precision-all.pdf}
		\caption{Precision \todo{and recall} of chunk retrieval with PBE, CTS and KWS compared with RLR}
		\label{fig:precision-all}
	\end{minipage}\hfill
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/precision-category-singularity-all.pdf}
		\caption{Precision \todo{and recall} of chunk retrieval with PBE, CTS and KWS compared with RLR for single and multiple categories present in the configuring I/O examples}
		\label{fig:precision-category-singularity-all}
	\end{minipage}
\end{figure}
\begin{figure}[htbp]
	\centering
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/success-all.pdf}
		\caption{Successful chunk retrievals for PBE, CTS, KWS and RLR}
		\label{fig:success-all}
	\end{minipage}\hfill
	\begin{minipage}{0.45\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/xxx.pdf}
		\caption{\todo{pointplot precision and recall for all techniques compared, also aganist example/category count?}}
		\label{fig:xxx}
	\end{minipage}
\end{figure}

\subsection{Comparing All Techniques}
Figure \ref{fig:precision-all}: PBE highest precision if extraction successful, also highest recall of all?. CTS still good also when not all information extracted

Figure \ref{fig:precision-category-singularity-all}: pbe very good for a single category, very bad for multilpe, performance of others quite similar for single vs. multiple categories, CTS slightly impacted, random benefits (<- do we need to explain that in text?)

Figure \ref{fig:success-all} pbe and kws best at extracting all desired lines, precision fig: pbe with higher precision

### 2019-11-05 thesis/txt/6-discussion.tex
describe more results for kws and all techniques, draft out conclusions section

\section{wip: best usage of single techniques}
\subsection{wip: best usage of PBE}
\subsection{wip: best usage of CTS}
\subsection{wip: best usage of KWS}

\section{wip:when to choose which technique}

>>>>

\section{wip: best usage of single techniques}

\subsection{wip: best usage of PBE}
\paragraph{wip: input}
when textual representation of blii to extract is only of one structural category. 1-3 examples enough.
\paragraph{wip: output usage}
very precise output & high recall if synthesis and extraction yields result: good for computer consumed retrievals.
If there is an output user can have high confidence it is the correct output.
Clearly detectable when there is no program synthesized / empty output -> system can go to fail-safe state.

\subsection{wip: best usage of CTS}
\paragraph{wip: input}
retrieval size factor 1 gives best balance of recall and precision, can handle different structural categories but bit of decline in retrieval quality, more examples do not improve quality in the number of examples we tested -> ir techniques commonly use a lot more examples for learning on
\paragraph{wip: output usage}

\subsection{wip: best usage of KWS}
\paragraph{wip: input}
category count has little influence -> suited if there is little prior knowledge on what the build failed / will fail. e.g. builds with a lot of steps and no pre-categorization of what step failed available
retrieval size factor: at least 1, more seems to have positive, but marginal influence
\paragraph{wip: output usage}
very low precision, only useful to filter lines in build log for further processing, e.g. reading by a developer

\section{wip:when to choose which technique}
TABLE!
\paragraph{wip: input}
number of categories:
one? -> pbe
two? -> CTS
more? -> KWS

availaable examples:

\paragraph{wip: output usage}
precision needed:

\begin{table}[htbp]
\begin{tabular}{ |c||c|c|c| }
  Technique & \multicolumn{3}{|c|}{Number of Categories in configuring examples} \\
  \hline
  & one & two & more \\
  PBE & yes & no & no \\ 
  CTS & yes & yes & no \\ 
  KWS & yes & yes & yes \\ 
  \hline
\end{tabular}
\caption{The small $1 \cdot 1$}
\label{tab:101}
\end{table}

\section{Threats to Validity}
chronologically selected examples -> very specific view, devs/users might pick more representative examples

very few evaluation runs with a high number of categories in configuring I/O examples -> because we chose to create such a ``realistic'' data set, from data set we see that many structural categories uncommon
